\section{Conclusion}
\label{sec:conclusion}

\subsection{Summary of Contributions}
This paper presented a real-time, web-based system for agricultural pest detection using a custom-trained YOLOv11 model. Our approach successfully addresses the limitations of traditional pest management methods by providing an automated, accurate, and accessible solution. Key contributions include the development of a custom-trained YOLOv11 model optimized for pest detection, implementation of a multi-modal web interface, and successful deployment using ONNX Runtime Web technology. The system achieved an overall mAP@0.5 of 0.87 with real-time inference capabilities of 16-22 FPS.

\subsection{Practical Viability and Impact}
The implemented user interface demonstrates the practical viability of the system, providing farmers and agricultural professionals with an intuitive tool for pest detection and monitoring. The dual-mode interface supporting both specialized pest detection and general object detection capabilities enhances the system's versatility in agricultural applications.

\subsection{Future Work}
Future research directions include:
\begin{itemize}
    \item Expanding the dataset to include a wider variety of pest species and crop types.
    \item Integrating the system with drone-based imaging for large-scale field monitoring.
    \item Developing a mobile application for offline pest detection in remote areas.
    \item Investigating the use of multi-spectral imaging to enhance detection accuracy.
\end{itemize}
