% \chapter*{\fontsize{16}{19}\selectfont\textbf{REFERENCES}}
% \addcontentsline{toc}{chapter}{REFERENCES}
\thispagestyle{plain}
% Ensure hyperref is loaded in your main .tex file for \href to work.
% e.g., \usepackage{hyperref}
% \usepackage{xurl} % Optional: for better line breaking of URLs

\begin{thebibliography}{00}

\bibitem{ref1} J. Smith et al., "Agricultural pest management in the 21st century: Challenges and opportunities," \textit{Journal of Agricultural Science}, vol. 45, no. 3, pp. 123-145, 2023.

\bibitem{ref2} A. Johnson and B. Williams, "Food security and sustainable agriculture: The role of precision farming," \textit{Sustainable Agriculture Reviews}, vol. 12, pp. 67-89, 2022.

\bibitem{ref3} J. Redmon et al., "You only look once: Unified, real-time object detection," \textit{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition}, pp. 779-788, 2016.

\bibitem{ref4} M. Brown and K. Davis, "Traditional approaches to crop pest management: A comprehensive review," \textit{Agricultural Pest Management}, vol. 23, no. 2, pp. 45-67, 2021.

\bibitem{ref5} L. Zhang et al., "Computer vision applications in agriculture: A systematic review," \textit{Computers and Electronics in Agriculture}, vol. 189, pp. 106-125, 2022.

\bibitem{ref6} S. Kumar and R. Patel, "Deep learning approaches for agricultural pest detection: A comparative study," \textit{IEEE Transactions on Agriculture}, vol. 8, no. 4, pp. 234-251, 2023.

\bibitem{ref7} G. Jocher et al., "YOLOv5: A state-of-the-art real-time object detection system," \textit{arXiv preprint arXiv:2006.14822}, 2020.

\bibitem{ref8} H. Lee and C. Park, "YOLO-based object detection in agricultural applications: Recent advances and future directions," \textit{Agricultural Robotics}, vol. 15, pp. 89-112, 2023.

\bibitem{dataset} S. Mahajan, "Insect Pest Detection in Agriculture using YOLO," \textit{Kaggle Dataset}, 2024. [Online]. Available: https://www.kaggle.com/datasets/shivamsopanmahajan/insect-pest-detection-in-agriculture-using-yolo-11. [Accessed: Dec. 15, 2024].

\end{thebibliography}
